A Machine Learning Approach to MLB Catcher Framing

### 2021-12-10 Slides.Rmd
Commit changes

```{r, echo=FALSE}
load("Model-Outputs/logistic-CM.Rda")
load("Model-Outputs/logistic-error.Rda")

conf_mx
1-error
```

@@

```{r}
data_no_catchers <- usable_data[, -18]

@@

```{r, message=FALSE}
#LASSO
lasso_fit <- glmnet(x[train, ], y[train], alpha = 1, lambda = lambda, family = 'binomial')
cv_lasso <- cv.glmnet(x[train, ], y[train], alpha = 1, family='binomial')

>>>>

```{r, echo=FALSE, cache=TRUE}
data_no_catchers <- usable_data[, -18]
train <- sample(1:nrow(data_no_catchers), nrow(data_no_catchers)/2)
test <- (-train)
log_reg_fit <- glm(strike ~ ., data=data_no_catchers[train, ], family='binomial')
pred <- predict.glm(log_reg_fit, type='response', newdata = data_no_catchers[test, ])
pred[pred >= 0.5] <- 'strike'
pred[pred < 0.5] <- 'ball'
```

```{r, cache=TRUE}
conf_mx <- table(pred=pred, true=data_no_catchers[test, ]$strike)
error <- (conf_mx[2] + conf_mx[3])/length(pred)
conf_mx
1-error
```

@@

```{r, cache=TRUE}
data_no_catchers <- usable_data[, -18]

@@

```{r, message=FALSE, cache=TRUE}
#LASSO
lasso_fit <- glmnet(x[train, ], y[train], alpha = 1, lambda = lambda, family = 'binomial')
cv_lasso <- cv.glmnet(x[train, ], y[train], alpha = 1, family='binomial')
